Speed and Precision in Range Analysis

### 2012-07-05 doc/Manuscript/CLSC/paper.tex
CLSC: Fixed authors and affiliation

\author{Victor Hugo Sperle Campos, Douglas do Couto Teixeira \\
Igor Rafael Assis Costa, Raphael Ernani Rodrigues and\\
Fernando Magno Quint\~{a}o Pereira%\corrauth
}

\address{UFMG -- 6627 Ant\^{o}nio Carlos Av, 31.270-010, Belo Horizonte, Brazil}

>>>>

%\author{Victor Hugo Sperle Campos, Douglas do Couto Teixeira \\
%Igor Rafael Assis Costa, Raphael Ernani Rodrigues and\\
%Fernando Magno Quint\~{a}o Pereira%\corrauth
%}

\author[llp]{Victor Hugo Sperle Campos}
\ead{victorsc@dcc.ufmg.br}

\author[llp]{Douglas do Couto Teixeira}
\ead{douglas@dcc.ufmg.br}

\author[llp]{Igor Rafael de Assis Costa}
\ead{igor@dcc.ufmg.br}

\author[llp]{Raphael Ernani Rodrigues}
\ead{raphael@dcc.ufmg.br}

\author[llp]{Fernando Magno Quint\~{a}o Pereira\corref{cor1}}
\ead{fernando@dcc.ufmg.br}

\cortext[cor1]{Corresponding author}

\address[llp]{UFMG -- 6627 Ant\^{o}nio Carlos Av, 31.270-010, Belo Horizonte, Brazil}
